### 2023-03-17 notebooks/fidelity.qmd
bloody hell

```{julia}
niter = 10
nsamples = 100
plts = []
for target in ce.data.y_levels
    # Search:
    generator = GenericGenerator()
    ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
    sampler = CCE.EnergySampler(ce;niter=niter, nsamples=100)
    Xgen = rand(sampler, nsamples)
    plt = plot(M, counterfactual_data, target=ce.target, xlims=(-5,5),ylims=(-5,5),cbar=false)
    scatter!(Xgen[1,:],Xgen[2,:],alpha=0.5,color=target,shape=:star,label="X|y=$target")
    push!(plts, plt)
end
plot(plts..., layout=(1,length(ce.data.y_levels)), size=(length(ce.data.y_levels)*300,300))
```

>>>>

```{julia}
niter = 10000
nsamples = 100
plts = []
for target in ce.data.y_levels
    # Search:
    generator = GenericGenerator()
    ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
    sampler = CCE.EnergySampler(ce;niter=niter, nsamples=100)
    Xgen = rand(sampler, nsamples)
    plt = plot(M, counterfactual_data, target=ce.target, xlims=(-5,5),ylims=(-5,5),cbar=false)
    scatter!(Xgen[1,:],Xgen[2,:],alpha=0.5,color=target,shape=:star,label="X|y=$target")
    push!(plts, plt)
end
plot(plts..., layout=(1,length(ce.data.y_levels)), size=(length(ce.data.y_levels)*300,300))
```
